---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Total number of steps

###First, we download the dataset, unzip it and make the dataframe of it.

```{r}
library (ggplot2)
URL<-"https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
    dir<-paste(getwd(),"/a.zip",sep="")#get url
    download.file(URL,dir)#upload file
    unzip(dir)#unzip file
    Frame<-read.csv("activity.csv")
    Frame$date<-as.POSIXct(Frame$date)
```
###Then we plot the number of steps by date. 
```{r}
C0<-aggregate(steps~date,data=Frame,FUN=sum)
    C0$date<-as.POSIXct(C0$date)
    ggplot(C0,aes(x=date,y=steps))+ geom_bar(stat="identity")
```
## Mean number of steps

###We also plot the mean number of steps.

```{r}
C1<-aggregate(steps~date,data=Frame,FUN=mean)
    C1$date<-as.POSIXct(C1$date)
    ggplot(C1,aes(x=date,y=steps))+ geom_line()+ggtitle("Average number f steps by date")
```

## Median number of steps

###We also plot the median number of steps by 5minute interval.As we see, during most of the 5minute intervals the number of steps was equal to zero.
```{r}
C2<-aggregate(steps~date,data=Frame,FUN=median)
    C2$date<-as.POSIXct(C2$date)
    ggplot(C2,aes(x=date,y=steps))+ geom_line()+ggtitle("Median number Of steps by date")
```
##Average number of steps
###We also plot average number of steps taken by interval
```{r}
C4<-aggregate(steps~interval,data=Frame,FUN=mean)
#plot average by INTERVAL
ggplot(C4,aes(x=interval,y=steps))+ geom_line()+ggtitle("Average number f steps by interval")
```
##Maximal number of steps
###We also find the 5minute interval where the number of steps is the largest
```{r}
Frame$date<-as.POSIXct(Frame$date)
d<-which.max(Frame[,1])
C<-c(as.character(Frame[d,2]), as.character(Frame[d,3]/100))
C
```
##Imputing missing values
###Number of missing values is
```{r}
sum(is.na(Frame$steps))
```
###Missing values are imputed by placing the median by the interval where NA was found instead of NA. Then, the histogram of total number of steps per day was made.
```{r}
Frame2<-Frame
Frame2$date<-as.POSIXct(Frame2$date)
Frame1<-aggregate(steps~interval,data=Frame2,FUN=median,na.rm=TRUE)#median by time
for(i in 1:dim(Frame2)[1])
{
  if(is.na(Frame2$steps[i]))
  {
   Frame2$steps[i]<-Frame1$steps[which(Frame2$interval[i]==Frame1$interval)][1]
  }
}
C0<-aggregate(steps~date,data=Frame2,FUN=sum)
```
##Total number of steps taken each day
```{r}
ggplot(C0,aes(x=date,y=steps))+ geom_bar(stat="identity")+ggtitle("Total number of steps taken each day")
```
##Median number of steps taken each day
```{r}
median(C0$steps,na.rm=TRUE)
```
##Mean number of steps taken per day 
```{r}
mean(C0$steps,na.rm=TRUE)
```
##Weekday and weekend patterns
All the days were identified as either weekdays or weekends. Dataframe was split and divided by 2 groups - weekends and weekdays.Then these data were plotted
```{r}
Frame2$weekday<-rep("weekday",dim(Frame2)[1])
for (i in (1:dim(Frame2)[1]))
{
  if((weekdays(Frame2$date[i])=="Sunday")|(weekdays(Frame2$date[i])=="Saturday"))
  {
    Frame2$weekday[i]="weekend"
  }
}
Frame2$weekday<-as.factor(Frame2$weekday)
Frame3<-split(Frame2,Frame2$weekday)


Weekend<-aggregate(steps~interval,data=Frame3$weekend,FUN=mean,na.rm=TRUE)

Weekday<-aggregate(steps~interval,data=Frame3$weekday,FUN=mean,na.rm=TRUE)
ggplot(Weekend,aes(x=interval,y=steps))+ geom_line()+ggtitle ("Mean number of steps in weekends")
ggplot(Weekday,aes(x=interval,y=steps))+ geom_line()+ggtitle ("Mean number of steps in weekdays")
```

