---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Total number of steps

###First, we download the dataset, unzip it and make the dataframe of it.

```{r}
library (ggplot2)
URL<-"https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
    dir<-paste(getwd(),"/a.zip",sep="")#get url
    download.file(URL,dir)#upload file
    unzip(dir)#unzip file
    Frame<-read.csv("activity.csv")
    Frame$date<-as.POSIXct(Frame$date)
```
###Then we plot the number of steps by date. 
```{r}
C0<-aggregate(steps~date,data=Frame,FUN=sum)
    C0$date<-as.POSIXct(C0$date)
    ggplot(C0,aes(x=date,y=steps))+ geom_bar(stat="identity")
```
## Mean number of steps

We also plot the mean number of steps.

```{r}
C1<-aggregate(steps~date,data=Frame,FUN=mean)
    C1$date<-as.POSIXct(C1$date)
    ggplot(C1,aes(x=date,y=steps))+ geom_line()+ggtitle("Average number f steps by date")
```

## Median number of steps

We also plot the median number of steps by 5minute interval.As we see, the number of steps was equal to zero during most of the 5minute intervals.
```{r}
C2<-aggregate(steps~date,data=Frame,FUN=median)
    C2$date<-as.POSIXct(C2$date)
    ggplot(C2,aes(x=date,y=steps))+ geom_line()+ggtitle("Median number Of steps by date")
```

## Average number of steps

We also plot average number of steps taken by interval
```{r}
C4<-aggregate(steps~interval,data=Frame,FUN=mean)
#plot average by INTERVAL
ggplot(C4,aes(x=interval,y=steps))+ geom_line()+ggtitle("Average number f steps by interval")
```

## Maximal number of steps
We also find the 5minute interval where the number of steps is the largest
```{r}
Frame$date<-as.POSIXct(Frame$date)
d<-which.max(Frame[,1])
C<-c(as.character(Frame[d,2]), as.character(Frame[d,3]/100))
C
```
## Imputing missing values
Number of missing values is
```{r}
sum(is.na(Frame$steps))
```
###Missing values are imputed by placing the median by the interval where NA was found instead of NA. 
```{r}
Frame2<-Frame
Frame2$date<-as.POSIXct(Frame2$date)
Frame1<-aggregate(steps~interval,data=Frame2,FUN=median,na.rm=TRUE)#median by time
for(i in 1:dim(Frame2)[1])
{
  if(is.na(Frame2$steps[i]))
  {
   Frame2$steps[i]<-Frame1$steps[which(Frame2$interval[i]==Frame1$interval)][1]
  }
}
C0<-aggregate(steps~date,data=Frame2,FUN=sum)
```
##Total number of steps taken each day
The histogram of the total number of steps per day was made. Mean and median number of steps are also displayed above
```{r}
ggplot(C0,aes(x=date,y=steps))+ geom_bar(stat="identity")+ggtitle("Total number of steps taken each day")+geom_hline(aes(yintercept=median(C0$steps,na.rm=TRUE), linetype="Median"), color = "blue",show.legend= TRUE)+geom_hline(aes(yintercept=mean(C0$steps,na.rm=TRUE), linetype="Mean"), color = "red",show.legend= TRUE) +scale_linetype_manual(name = "number of steps", values = c(2, 2), 
guide = guide_legend(override.aes = list(color = c("blue", "red"))))

```

 Median number of steps taken each day is
```{r}
median(C0$steps,na.rm=TRUE)
```
 
 Mean number of steps taken per day is
```{r}
mean(C0$steps,na.rm=TRUE)
```
## Weekday and weekend patterns
All the days were identified as either weekdays or weekends. Dataframe was split and divided by 2 groups - weekends and weekdays.Then these data were plotted
```{r}
Frame2$weekday<-rep("weekday",dim(Frame2)[1])
invisible( Sys.setlocale("LC_ALL","English"))
for (i in (1:dim(Frame2)[1]))
{
  if((weekdays(Frame2$date[i])=="Sunday")|(weekdays(Frame2$date[i])=="Saturday"))
  {
    Frame2$weekday[i]="weekend"
  }
}
Frame2$weekday<-as.factor(Frame2$weekday)
Frame3<-split(Frame2,Frame2$weekday)

##split надо корректно
Weekend<-aggregate(steps~interval,data=Frame3$weekend,FUN=mean,na.rm=TRUE)

Weekday<-aggregate(steps~interval,data=Frame3$weekday,FUN=mean,na.rm=TRUE)
ggplot(Weekend,aes(x=interval,y=steps))+ geom_line()+ggtitle ("Mean number of steps in weekends")
ggplot(Weekday,aes(x=interval,y=steps))+ geom_line()+ggtitle ("Mean number of steps in weekdays")
```

